Posterior summarisation in Bayesian phylogenetics using Tracer 1.7

### 2017-09-16 manuscript/tracer17.tex
bump version to 1.7

% Title must be 150 characters or less
\title[Tracer 1.6]{Posterior summarisation in Bayesian phylogenetics using Tracer 1.6}

@@

\section{Motivation:}
%Computational evolutionary biology, statistical phylogenetics and coalescent-based population genetics are becoming increasingly central to the analysis and understanding of molecular sequence data.
Bayesian inference of phylogeny using Markov chain Monte Carlo (MCMC) plays a central role in understanding evolutionary history and processes from molecular sequence data.
Visualising and analysing the samples from the posterior distribution is a key step in any non-trivial Bayesian inference, and it is especially important for methods that employ MCMC.
\section{Results:}
Here we present a software package \emph{Tracer} (version 1.6) for visualising and analysing the trace files generated by Bayesian MCMC runs.
The \emph{Tracer} software also provides kernel density estimation, cheap marginal likelihood estimation,
multivariate visualisation, demographic trajectory reconstruction, conditional posterior distribution summary and more.
\section{Availability:}
Tracer is open-source under the GNU lesser general public license and available at
\url{http://beast.bio.ed.ac.uk/Tracer} and \url{https://github.com/beast-dev/tracer}.

@@

Bayesian inference of phylogeny using Markov chain Monte Carlo (MCMC) \citep{rannala1996probability,mau1999bayesian} flourishes as a popular approach to uncover the evolutionary relationships among taxa, whether genes, genomes, individuals or species.
MCMC approaches generate samples of model parameter values including the phylogenetic tree drawn from their posterior distribution given molecular sequence data.
Visualising, tabulating and marginalising these samples is critical for approximating the posterior quantities of interest that one reports in a Bayesian phylogenetic analysis.
%However, the full posterior distribution is high-dimensional and often difficult to visualise.
To facilitate this task, we develop the Tracer (version 1.6) software package that parses MCMC log files of samples to interactively explore the high-dimensional posterior distribution.
%
%containing the list of parameters whose values sampled from the chain.
Tracer works automatically with sample output from
%It can be used to analyse runs of
BEAST 1 \citep{drummond2012bayesian}, BEAST 2 \citep{bouckaert2014beast2}, MrBayes \citep{ronquist2012mrbayes}, RevBayes \citep{hohna2016revbayes}, LAMARC \citep{kuhner2006lamarc}, Migrate \citep{beerli2006comparison} and possibly other MCMC programs from other domains.

@@

% MAS: We need to limit the number of figures
%\begin{figure}[ht]
%\centerline{
%\includegraphics[width=0.45\textwidth]{./figures/tracer.pdf}
%}
%\caption{The system design of Tracer 1.6}
%\label{fig:tracer}
%\end{figure}

@@

%\section*{References}
% The bibtex filename
\bibliographystyle{natbib}
\bibliography{tracer16}

>>>>

% Title must be 150 characters or less
\title[Tracer 1.7]{Posterior summarisation in Bayesian phylogenetics using Tracer 1.7}

@@

\section{Motivation:}
%Computational evolutionary biology, statistical phylogenetics and coalescent-based population genetics are becoming increasingly central to the analysis and understanding of molecular sequence data.
Bayesian inference of phylogeny using Markov chain Monte Carlo (MCMC) plays a central role in understanding evolutionary history and processes from molecular sequence data.
Visualising and analysing the samples from the posterior distribution is a key step in any non-trivial Bayesian inference, and it is especially important for methods that employ MCMC.
\section{Results:}
Here we present a software package \emph{Tracer} (version 1.7) for visualising and analysing the trace files generated by Bayesian MCMC runs.
The \emph{Tracer} software also provides kernel density estimation, cheap marginal likelihood estimation,
multivariate visualisation, demographic trajectory reconstruction, conditional posterior distribution summary and more.
\section{Availability:}
Tracer is open-source under the GNU lesser general public license and available at
\url{http://beast.bio.ed.ac.uk/Tracer} and \url{https://github.com/beast-dev/tracer}.

@@

Bayesian inference of phylogeny using Markov chain Monte Carlo (MCMC) \citep{rannala1996probability,mau1999bayesian} flourishes as a popular approach to uncover the evolutionary relationships among taxa, whether genes, genomes, individuals or species.
MCMC approaches generate samples of model parameter values including the phylogenetic tree drawn from their posterior distribution given molecular sequence data.
Visualising, tabulating and marginalising these samples is critical for approximating the posterior quantities of interest that one reports in a Bayesian phylogenetic analysis.
%However, the full posterior distribution is high-dimensional and often difficult to visualise.
To facilitate this task, we develop the Tracer (version 1.7) software package that parses MCMC log files of samples to interactively explore the high-dimensional posterior distribution.
%
%containing the list of parameters whose values sampled from the chain.
Tracer works automatically with sample output from
%It can be used to analyse runs of
BEAST 1 \citep{drummond2012bayesian}, BEAST 2 \citep{bouckaert2014beast2}, MrBayes \citep{ronquist2012mrbayes}, RevBayes \citep{hohna2016revbayes}, LAMARC \citep{kuhner2006lamarc}, Migrate \citep{beerli2006comparison} and possibly other MCMC programs from other domains.

@@

% MAS: We need to limit the number of figures
%\begin{figure}[ht]
%\centerline{
%\includegraphics[width=0.45\textwidth]{./figures/tracer.pdf}
%}
%\caption{The system design of Tracer 1.7}
%\label{fig:tracer}
%\end{figure}

@@

%\section*{References}
% The bibtex filename
\bibliographystyle{natbib}
\bibliography{tracer17}
